---
title: "Homework 1"
output: github_document
---

I'm an R Markdown document! 
```{r}
library(tidyverse)
library(ggplot2)
```

# Problem One

```{r}
data("penguins", package = "palmerpenguins")
mean(penguins$flipper_length_mm,na.rm=TRUE)
```
The dataset contains the information on penguins. Each observation is a penguin and there are eight columns containing the information species, the island they are from, bill length (in mm), bill depth (in mm), flipper length (in mm), body mass (in g), sex and year for each penguin observation.
There are `r nrow(penguins)` rows and `r ncol(penguins)` columns in the penguins dataset. 
The mean of flipper length is `r mean(pull(penguins , flipper_length_mm),na.rm=TRUE)`mms after removing the missing values.

```{r}
ggplot(penguins,aes(x = bill_length_mm, y = flipper_length_mm, color = species))+ geom_point()
ggsave("hw1_scatter_plot.pdf", height = 4, width = 6)
```
# Problem Two

```{r}
problem2_df = tibble(
  norm_samp = rnorm(10),
  norm_samp_pos = norm_samp > 0,
  char_vec = c("a","b","c","d","e","f","g","h","i","j"),
  factor_vec = factor(c("high","medium","low","high","medium","low","high","medium","low","high"))
)
```

```{r}
mean_vector1 = mean(pull(problem2_df,norm_samp))
mean_vector1
mean_vector2 = mean(pull(problem2_df,norm_samp_pos))
mean_vector2
mean_vector3 = mean(pull(problem2_df,char_vec))
mean_vector3
mean_vector4 = mean(pull(problem2_df,factor_vec))
mean_vector4
```

```{r}
as.numeric((pull(problem2_df,norm_samp)))
as.numeric((pull(problem2_df,norm_samp_pos)))
as.numeric((pull(problem2_df,char_vec)))
as.numeric((pull(problem2_df,factor_vec)))
```
```

