---
title: "Homework 1"
output: github_document
---

I'm an R Markdown document! 
```{r}
#default setting echo is true
knitr::opts_chunk$set(echo = TRUE)
#load the libraries
library(tidyverse)
library(ggplot2)
```

# Problem One

```{r}
#load the penguins dataset
data("penguins", package = "palmerpenguins")
#Take a look at the dataset
head(penguins)
#get the name
names(penguins)
#look at the summary of data
summary(penguins)
#Get the nrow and ncol
penguins_row = nrow(penguins)
penguins_col = ncol(penguins)
#Calculate the mean flipper length
mean_of_flipper_length = mean(penguins$flipper_length_mm,na.rm=TRUE)
```

Description:
The dataset contains the information on three species of penguins from three islands. The mean of bill_length_mm is 43.92mm. The mean of bill_depth_mm is 200.9mm. The mean of body_mass_g is 4202g. Each row(observation) is a penguin and there are eight columns containing the information of penguins including species, the island they are from, bill length (in mm), bill depth (in mm), flipper length (in mm), body mass (in g), sex and year for each penguin observation.
There are `r nrow(penguins)` rows and `r ncol(penguins)` columns in the penguins dataset. 
The mean of flipper length is `r mean(pull(penguins , flipper_length_mm),na.rm=TRUE)`mms after removing the missing values.

```{r}
#Creating the scatterplot with ggplot
ggplot(penguins,aes(x = bill_length_mm, y = flipper_length_mm, color = species))+ geom_point()
ggsave("hw1_scatter_plot.pdf", height = 4, width = 6)
```
# Problem Two

```{r}
#create the dataframe for problem 2
problem2_df = tibble(
  #create the normal sample
  norm_samp = rnorm(10),
  #create the logical vector
  norm_samp_pos = norm_samp > 0,
  #create the character vector
  char_vec = c("a","b","c","d","e","f","g","h","i","j"),
  #create the factor vector
  factor_vec = factor(c("high","medium","low","high","medium","low","high","medium","low","high"))
)
```

```{r}
#calculate mean for the normal sample of size 10
mean_vector1 = mean(pull(problem2_df,norm_samp))
mean_vector1
#calculate mean for the logical vector
mean_vector2 = mean(pull(problem2_df,norm_samp_pos))
mean_vector2
#calculate mean for the character vector
mean_vector3 = mean(pull(problem2_df,char_vec))
mean_vector3
#calculate mean for the factor vector
mean_vector4 = mean(pull(problem2_df,factor_vec))
mean_vector4
```

The mean can be calculated for the number vector(the normal sample of size 10) and the logical vector. But the mean cannot be calculated for the character vector and the factor vector and the result is N/A for the character vector and the factor vector.

```{r,eval = FALSE}
#use as.numeric to create three new vector from the three vectors above
#and try to calculate the mean value of them
numeric_logical_vector = as.numeric((pull(problem2_df,norm_samp_pos)))
mean(numeric_logical_vector)
numeric_char_vector = as.numeric((pull(problem2_df,char_vec)))
mean(numeric_char_vector)
numeric_factor_vector =as.numeric((pull(problem2_df,factor_vec)))
mean(numeric_factor_vector)
```

The values of logical factor are converted to numbers 1 and 0, since the value of TRUE is 1 and the value of FALSE is 0 in R programming. The values factor vector are converted to numbers of 1, 2 and 3. But the character vector cannot be converted to numbers.
Yes, this explained why we can calculate the mean of the logical vector in the question above since TRUE and FALSE have values of 1 and 0. And we cannot calculate the mean for the factor vector unless it is converted to number using as.numeric. And for the character vector, it cannot be converted to numbers because here they are letters instead of numbers in the character vector.